# Introduction {#intro}

## Preliminary

The use of SPSS accommodates all people including the novice computer user and those with no previous experience using SPSS. The study chapters are divided into sub-sections that explains the statistics to be used, with underlying assumptions, and methodology for the results interpretation and express then in a research report. 

The genesis of the book explains how to start the SPSS, variable definitions, data entry and saving. All the necessary and fundamental statistics techniques are explained. These statistics included the descriptive statistics, data graphing, association and prediction, inferential statistics for parametric and nonparametric, and statistics for test construction.

The learners are expected to follow up with the sample screenshots. 

New to this edition 1:

Data and real output are now available for all Phrasing Results sections – eliminating hypothetical output or hypothetical data

Henry Njagi is a lecturer and a Statistician with advanced knowledge in data and Analytics (MSc. in Applied Statistics, Jomo Kenyatta University of Agriculture and Technology).

```{r nice-fig, fig.cap='Here is a nice figure!', out.width='80%', fig.asp=.75, fig.align='center'}
par(mar = c(4, 4, .1, .1))
plot(pressure, type = 'b', pch = 19)
```

Reference a figure by its code chunk label with the `fig:` prefix, e.g., see Figure \@ref(fig:nice-fig). Similarly, you can reference tables generated from `knitr::kable()`, e.g., see Table \@ref(tab:nice-tab).

```{r nice-tab, tidy=FALSE}
knitr::kable(
  head(iris, 20), caption = 'Here is a nice table!',
  booktabs = TRUE
)
```

You can write citations, too. For example, we are using the **bookdown** package [@R-bookdown] in this sample book, which was built on top of R Markdown and **knitr** [@xie2015].
